Figures

### 2019-07-03 figures/07_model-selection.Rmd
use transparent backgrounds

```{r tp_re}
fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  ylab("TP model, pasture RE slope") + theme(legend.position = 0)

@@

```{r tn_re}
# dotplot tn hu4 random effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  ylab("TN model, corn RE slope") + theme(legend.position = 0)

@@

dt_predictors <- dplyr::filter(dt, key %in% 
                                 c("tp",
                                   "nitrogen_atmospheric_deposition",
                                   "clay_pct"))
dt_modelled <- dplyr::filter(dt, key %in% 
                               c("maxdepth", "tn", "soil_org_carbon",
                                 "buffer_cultivated_crops", "corn",
                                 "nitrogen_fertilizer_use"))

gg_hist <- ggplot(data = dt_predictors) + 
  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
  geom_vline(aes(xintercept = median, color = signif_hu4), 
             linetype = "dashed") +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  theme(legend.position = 0) +
  facet_wrap(~key)

@@

gg_tp <- ggplot(data = dt) + 
  geom_point(aes(x = tn, y = tp, color = signif_hu4)) +
  geom_line(stat = "smooth", method = lm, se = FALSE, 
            aes(x = tn, y = tp, color = signif_hu4)) +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  theme(legend.position = 0)

@@

lg <- lagosne_load("1.087.1")
gg_line <- fit_tn$re %>%
  ungroup() %>%
  mutate(hu4vzoneid = paste0("HU4_", hu4vzoneid)) %>%
  left_join(dplyr::select(lg$hu4.chag, 
                          hu4_zoneid, hu4_dep_totaln_2010_mean), 
            by = c("hu4vzoneid" = "hu4_zoneid")) %>%
ggplot() +
  geom_pointrange(aes(x = hu4_dep_totaln_2010_mean, y = `50%`,
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  theme_cowplot() +
  ylab("TN model, corn RE slope") + xlab("N deposition") +
  theme(legend.position = 0)

>>>>

```{r tp_re}
fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TP model, pasture RE slope") + theme(legend.position = 0)

@@

```{r tn_re}
# dotplot tn hu4 random effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TN model, corn RE slope") + theme(legend.position = 0)

@@

dt_predictors <- dplyr::filter(dt, key %in% 
                                 c("tp",
                                   "nitrogen_atmospheric_deposition",
                                   "clay_pct")) %>%
  dplyr::left_join(pred_key, by = c("key" = "var"))
dt_predictors[is.na(dt_predictors$pretty), "pretty"] <- 
  sapply(dt_predictors[is.na(dt_predictors$pretty), "key"], toupper)

dt_modelled <- dplyr::filter(dt, key %in% 
                               c("maxdepth", "tn", "soil_org_carbon",
                                 "buffer_cultivated_crops", "corn",
                                 "nitrogen_fertilizer_use"))

gg_hist <- ggplot(data = dt_predictors) + 
  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
  geom_vline(aes(xintercept = median, color = signif_hu4), 
             linetype = "dashed") +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  cowplot::theme_cowplot() +
  theme(legend.position = 0) +
  theme(rect = element_rect(fill = "transparent"), 
        strip.background = element_rect(fill = "white"), 
        strip.text = element_text(face = "bold")) +
  facet_wrap(~pretty)

@@

gg_tp <- ggplot(data = dt) + 
  geom_point(aes(x = tn, y = tp, color = signif_hu4)) +
  geom_line(stat = "smooth", method = lm, se = FALSE, 
            aes(x = tn, y = tp, color = signif_hu4)) +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  cowplot::theme_cowplot() +
  theme(legend.position = 0) + 
  theme(rect = element_rect(fill = "transparent"))

@@

lg <- lagosne_load("1.087.1")
gg_line <- fit_tn$re %>%
  ungroup() %>%
  mutate(hu4vzoneid = paste0("HU4_", hu4vzoneid)) %>%
  left_join(dplyr::select(lg$hu4.chag, 
                          hu4_zoneid, hu4_dep_totaln_2010_mean), 
            by = c("hu4vzoneid" = "hu4_zoneid")) %>%
ggplot() +
  geom_pointrange(aes(x = hu4_dep_totaln_2010_mean, y = `50%`,
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  theme_cowplot() +
  ylab("TN model, corn RE slope") + xlab("N deposition") +
  cowplot::theme_cowplot() +
  theme(legend.position = 0) + 
  theme(rect = element_rect(fill = "transparent"))
